Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-07-21 docs/paper/paper.Rmd
add incidence rate discussion across ECDC/UK

- Incidence in the ECDC
  - Omicron variant
  - BA.1 and BA.2 variant
  - Differences across countries and timings
  - NPIs across countries
  - testing across countries

>>>>

In our study period, incidence rates across ECDC nations and in the UK were primary driven by the spread of noval subvariants of concern related to the Omicron variant. Many nations, such as the UK saw large BA.1 waves in early January to late January that then resulted in declining incidence rates through Febuary. From late Febuary, througth to the end of May, most nations then saw another wave, typically with lower reported incidence rates, driven by BA.2. This wave was typically characterised by a lower peak than the BA.1 wave but a longer tail. The end of our study period was characterised by the gradual take-over of the BA.4/BA.5 subvariants that again had a lower peak and lower absolute growth rates. Unlike earlier periods in the pandemic, our study period did not see the use of new non-pharmaceutical interventions (NPIs) in response to increasing COVID-19 incidence in most locations. In addition, in general ascertainment rates likely reduced over time in most locations due to reductions in routine testing, and reductions in test availability. Whilst both the reduced use of NPIs and testing generally occured across nations our study period also marked an increase in the heterogenity of the response to COVID-19 pandemic with nations changing policy at different times and to different degrees. This is in contrast to the early COVID-19 pandemic response for which most nations took similar actions at similar times.
